---
title: "Statistical Analysis"
author: "S.McDowell"
date: "8/13/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load library's
```{r}
library(ggplot2)
library(tinytex)
```

### Overview
This project you will investigate the exponential distribution in R and compare it with the Central Limit Theorem.

### Simulations
```{r sims}
set.seed(12344321)
#Means
mns = NULL
lambda <- 0.2
n <- 40
for (i in 1:1000) mns = c(mns, mean(rexp(n,rate = lambda)))
```

### Sample Mean versus Theoretical Mean
```{r means}
#Means
hist(mns,breaks = 40,col = "cyan", main = "The Distribution of 1000 Averages from 40 Exponentials",xlab = "Mean Values")
sample_mean <- mean(mns)
sample_mean
th_mean<- 1/lambda
th_mean
abline(v = th_mean, col="blue",lwd = 3)
legend("topright",col = "blue", lty = 1, lwd = 3, legend = "Theoretical Mean" )
```

We see that the sample mean and the theoretical mean are very similar.

### Sample Variance versus Theoretical Variance
```{r vars}
#Variances
exp_sd <- (1/lambda)/sqrt(n)
paste("The theoretical standard deviation is",exp_sd, sep = ",")
exp_var <- (exp_sd)^2
paste("The theoretical variance is",exp_var, sep = ",")

sample_sd <- sd(mns)
paste("The sample standard deviation is",sample_sd, sep = ",")
sample_var <- var(mns)
paste("The sample standard variance is",sample_var, sep = ",")
```
We see that the sample standard deviation and sample variance are close approximations of the theoretical standard deviation and variance.

### Distribution
```{r compare}
fit <- seq(min(mns),max(mns), length=100)
standard_fit <- dnorm(fit,mean =th_mean,sd=exp_sd )

hist(mns,breaks = n,col = "cyan",prob=T, main = "Distribution of Means",xlab = "Mean Values")
lines(fit, standard_fit,pch = 2, col="blue",lwd=5)
```

Here we have the distribution of means overlayed with an normal cure indication that the simulation means are normally distributed.
